\documentclass{resume} % Use the custom resume.cls style
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[backend=bibtex, style=numeric, sorting=ydnt, maxnames=99, maxcitenames=99]{biblatex}
\addbibresource{ref.bib}
\usepackage{palatino}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.1in]{geometry} % Document margins

\name{Wei Guo}
\address{Personal website: \href{https://alexandreguo2001.github.io/}{\texttt{alexandreguo2001.github.io}}}
\address{
    \href{https://scholar.google.com/citations?user=0r_TzzkAAAAJ&hl=en}{Google Scholar} \\ 
    \href{https://github.com/AlexandreGUO2001/}{Github} \\
    \href{https://www.linkedin.com/in/wei-guo-264b97293/}{LinkedIn}
}
\address{Email: \href{mailto:wei.guo@gatech.edu}{\texttt{wei.guo@gatech.edu}}}


\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{black}{\textsc{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
\setlength{\leftmargin}{1.5em}
}
\item[]
}{
\end{list}
}



\begin{document}
\begin{rSection}{Education}
{\bf \href{https://www.gatech.edu/}{Georgia Institute of Technology}, \href{https://ml.gatech.edu/}{Machine Learning Center}} \hfill {\em Aug 2023 -- Present} 
\\ Ph.D. in Machine Learning\hfill
\\ \textbf{Advisor}: Professors \href{https://yongxin.ae.gatech.edu/}{Yongxin Chen} and \href{https://mtao8.math.gatech.edu/index.html}{Molei Tao}

{\bf \href{https://www.pku.edu.cn/}{Peking University}, \href{https://www.math.pku.edu.cn/}{School of Mathematical Sciences}} \hfill {\em Sep 2019 -- Jul 2023} 
\\ B.S. in Statistics
\\ \textbf{GPA}: 3.848/4.0; rank: 5/44 \hfill
\\ \textbf{Advisor}: Professor \href{https://zcrabbit.github.io/}{Cheng Zhang} 
\end{rSection}

\begin{rSection}{Research Interests}
    \begin{itemize}[leftmargin=0in]
        \item \textbf{Statistics and Probability}: Theoretical analysis and practical design of sampling algorithms (Markov Chain Monte Carlo, non-equilibrium (e.g., denoising diffusion, stochastic localization) sampling, or learning-based neural samplers); Applied stochastic analysis with applications to optimal transport, stochastic optimal control, and statistical physics.
        \item \textbf{Machine Learning}: Generative modeling, with a particular focus on (continuous/discrete) diffusion and flow-based models and with applications to vision and language.
    \end{itemize}
\end{rSection}


% \begin{rSection}{Research Experience}
% \begin{rSubsection}{Project name 1 \cite{paper1}}{Jan 2024 - Present}{Supervisors: \href{https://example.com/}{Dr. A}, \href{https://example.com/}{Prof. B}, and \href{https://example.com/}{Prof. C}}{CMU}
% \item Proposed ...
% \item Found ...
% \item Completed ...
% \item Modified ...
% \item Proposed ...
% \item Finished ...
% \end{rSubsection}


% \begin{rSubsection}{Project name 2 \cite{paper2}}{Dec 2023 - Feb 2024}{Supervisors: \href{https://example.weebly.com/}{Dr. A} and \href{https://www.ece.cmu.edu/directory/bios/example}{Prof. B}}{CMU}
% \item Ran experiments for ...
% \item Organized ...
% \item Explored ... 
% \item Proposed ...
% \item Finished ...
% \end{rSubsection}
% \end{rSection}


\begin{rSection}{Preprints and Publications} 
    (In reversed chronological order. $^*$ denotes equal contribution or alphabetical order.)
    \itemsep -2pt
    \nocite{*}\leavevmode\printbibliography[heading=none]
\end{rSection}



\begin{rSection}{Teaching Assistant} \itemsep -2pt
\href{https://ae3531a.notion.site/Course-Syllabus-Fall-2024-049faa69bedb4dd2b9b353318f52d5d6}{AE 3531: Control System Analysis and Design}. 
Lecturer: \href{https://research.gatech.edu/people/lu-gan}{Lu Gan}.
\hfill {\em Fall 2024} \\
AE 8803: Optimal Transport Theory and Applications. 
Lecturer: \href{https://yongxin.ae.gatech.edu/}{Yongxin Chen}.
\hfill {\em Spring 2025} \\
AE 3530: System Dynamics and Vibration.
Lecturer: \href{https://yongxin.ae.gatech.edu/}{Yongxin Chen}.
\hfill {\em Fall 2025} \\
\end{rSection}


\begin{rSection}{Community Service} \itemsep -2pt
    Served as a reviewer for ICLR 2024 (1 paper), ICLR 2025 (3 papers), and NeurIPS 2025 (5 papers).
\end{rSection}




\begin{rSection}{Awards} \itemsep -2pt
    PKU merit student in the academic year of 2019-2020 \hfill {\em Oct 2020} \\
    PKU merit student pacesetter in the academic year of 2020-2021 \hfill {\em Oct 2021} \\
    PKU merit student in the academic year of 2021-2022 \hfill {\em Oct 2022} \\
    2023 Beijing Outstanding Undergraduate Graduate Award \hfill {\em Jul 2023} \\
    Best poster award at Yale FDS conference ``Recent Advances and Future Directions for Sampling'' \\
    \phantom{.} \hfill {\em Oct 2024} \\
\end{rSection}


    
\begin{rSection}{Technical Skills} \itemsep -2pt
\begin{itemize}[leftmargin=0in]
    \item \textbf{Mathematics and Statistics}: Markov chain Monte Carlo, convex optimization, stochastic analysis, optimal transport, applied partial differential equations.
    \item \textbf{Machine learning}: computer vision, natural language processing.
    \item \textbf{Programming}: proficient programming in Python (including PyTorch).
    \item \textbf{Languages}: Chinese (Mandarin and Wu dialect, native), English (proficient), French (beginner).
\end{itemize}


\end{rSection}
\end{document}